---
title: "Penalties for Adjusting Public Policies are Stubborn"
subtitle: Replication code for paper and SI tables and figures
author: Felix Hartmann, Ferdinand Geissler, Macartan Humphreys, Heike Klüver, Johannes Giesecke
output-file: analysis.html
format:
  html:
    number-sections: true
    embed-resources: true
    toc: true
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
---

This file reproduces paper and SI tables and figures. Theory figures 1–2 are produced by `theory.qmd`. Object names in the first column jump to the section that produces that object.

| Object | Overleaf file name | Overleaf label |
|:-------|:-------------------|:---------------|
| [Table 1](#tbl-likelihoods) | — (inlined in `main.tex`) | `likelihoods` |
| [Figure 1](#fig-policy) | `2_figures/policy.pdf` | `fig:policy` |
| [Figure 2](#fig-credibility) | `2_figures/credibility.pdf` | `fig:credibility` |
| [Figure 3](#fig-prior) | `2_figures/figure_10.pdf` | `fig:Prior` |
| [Table 2](#tbl-example) | — (inlined in `main.tex`) | `tab:example` |
| [Figure 4](#fig-raw) | `2_figures/raw_disagg.pdf` | `fig:raw` |
| [Table 3](#tbl-saturated) | `1_tables/tab_1_full.tex` | `table:saturated` |
| [Figure 5](#fig-itt) | `2_figures/figure_1.pdf` | `fig:ITT` |
| [Figure 6](#fig-science-information) | `2_figures/figure_3_new.pdf` | `fig:ScienceInformation` |
| [Table A.1](#tbl-coefficients-policy) | — (inlined in `appendix.tex`) | `table:coefficients:policy` |
| [Figure A.1](#fig-policy-updating) | `2_figures/fig_pol_updating.pdf` | `fig:policy:updating` |
| [Figure C.1](#fig-c1) | `2_figures/Screenshot_2021-09-08 Umfrage(1–5).png` | — |
| [Figure C.2](#fig-c2) | `2_figures/Screenshot_2021-09-08 Umfrage(6–8).png` | — |
| [Table D.1](#tbl-d1) | — (inlined in `appendix.tex`) | — |
| [Figure D.1](#fig-priors) | `2_figures/figure_13.pdf` | `fig:priors` |
| [Table E.1](#tbl-e1) | — (inlined in `appendix.tex`) | — |
| [Table E.2](#tbl-treatment-compliance) | — (inlined in `appendix.tex`) | `TreatmentCompliance` |
| [Table E.3](#tbl-coefficients) | `1_tables/tab_man1` | `table:coefficients` |
| [Table F.1](#tbl-inquiry-reconciliation) | — (inlined in `appendix.tex`) | `tab:inquiry_reconciliation` |
| [Table F.2](#tbl-parameter-mapping) | — (inlined in `appendix.tex`) | `tab:parameter_mapping` |
| [Table F.3](#tbl-answer-strategy) | — (inlined in `appendix.tex`) | `tab:answer_strategy` |
| [Table G.1](#tbl-saturated-0) | `1_tables/tab_1_full_0.tex` | `table:saturated_0` |
| [Table G.2](#tbl-saturated-1) | `1_tables/tab_1_full_1.tex` | `table:saturated_1` |
| [Table G.3](#tbl-saturated-priors) | `1_tables/tab_1_full_priors.tex` | `table:saturated_priors` |
| [Table G.4](#tbl-saturated-priors-interactions) | `1_tables/tab_1_full_priors_interactions` | `table:saturated_priors_interactions` |
| [Figure G.1](#fig-cate-priors) | `2_figures/fig_1.pdf` | `fig:cate_priors` |
| [Table G.5](#tbl-saturated-high-priors) | `1_tables/tab_1_high_priors.tex` | `tab:saturated_high_priors` |
| [Table G.6](#tbl-saturated-med-priors) | `1_tables/tab_1_med_priors.tex` | `tab:saturated_med_priors` |
| [Table G.7](#tbl-saturated-low-priors) | `1_tables/tab_1_low_priors.tex` | `tab:saturated_low_priors` |
| [Table G.8](#tbl-g8) | — (inlined in `appendix.tex`) | — |
| [Table G.9](#tbl-g9) | — (inlined in `appendix.tex`) | — |

# 1. Housekeeping

```{r}
#| label: housekeeping

rm(list = ls())
set.seed(201911)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment = NA)

if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman")
pacman::p_load(
  estimatr,
  broom,
  texreg,
  haven,
  tidyverse,
  knitr,
  kableExtra,
  gridExtra,
  interplot
)

fig_dir <- "2_figures"
input_dir <- "1_input"
dir.create(fig_dir, showWarnings = FALSE)

# Survey `.sav` and election `.dta` are external; OxCGRT is fetched unless a local CSV is set.
data_dir <- Sys.getenv(
  "INCONSISTENCY_DATA_DIR",
  unset = file.path(
    "..", "..", "Covid Vaccine Allocation", "4_data", "wave_3", "final"
  )
)
survey_file <- file.path(
  data_dir,
  "D-P21-13185 HU Berlin Impfskeptiker_Welle 3_Finaler Datensatz.sav"
)
vignette_file <- file.path(input_dir, "W3_exp5_vignettes_universe.dta")

election_file <- Sys.getenv(
  "INCONSISTENCY_ELECTION_DTA",
  unset = file.path(
    "..", "..", "Covid Vaccine Allocation",
    "5_writing", "Paper 4 Inconsistency", "1_analysis",
    "1_input", "dataverse_files", "covid19_replication.dta"
  )
)
oxcgrt_url <- "https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker-legacy/main/legacy_data_202207/OxCGRT_latest.csv"
oxcgrt_csv <- Sys.getenv("INCONSISTENCY_OXCGRT_CSV", unset = "")

stopifnot(file.exists(survey_file))
stopifnot(file.exists(vignette_file))
stopifnot(file.exists(election_file))

outcomes <- c(
  "credible", "competent", "correct",
  "convinced_of_message_2", "behave_as_message_2"
)
mod_names <- c(
  "Credible", "Competent", "Correct",
  "Belief (msg 2)", "Behave (msg 2)"
)
outcome_labels <- mod_names

# Lin (2013) demeaning is applied only inside model helpers.
# The analysis data keep 0/1 treatments.
treatment_vars <- c("inconsistent", "trusted", "science", "safe_time1")

prior_low <- 3.3
prior_high <- 6.6
```

# 2. Helpers

Demeaning is not applied to the stored data. `with_demeaned_treatments()` subtracts sample means of the listed 0/1 treatments on a *copy* used only for fitting. After [Lin (2013)](https://doi.org/10.1214/12-AOAS583), the coefficient on a demeaned treatment is the average effect. Subgroup models demean within the subgroup because the helper is called on the filtered data.

```{r}
#| label: helpers

with_demeaned_treatments <- function(data, vars = treatment_vars) {
  present <- intersect(vars, names(data))
  data |>
    mutate(across(all_of(present), \(x) as.numeric(x) - mean(as.numeric(x), na.rm = TRUE)))
}

fit_saturated <- function(data, y, rhs = "inconsistent * trusted * science * safe_time1") {
  d <- with_demeaned_treatments(data)
  estimatr::lm_robust(as.formula(paste(y, "~", rhs)), data = d)
}

fit_saturated_list <- function(data, y_vec = outcomes, rhs = "inconsistent * trusted * science * safe_time1") {
  lapply(y_vec, function(y) fit_saturated(data, y, rhs))
}

table_note_outcomes <- paste(
  "\\item %stars. Treatments are demeaned (Lin 2013) so reported coefficients are average effects.",
  "Belief (msg 2) is conviction of the second message, recoded so that higher values mean greater agreement with the second recommendation --- not belief updating (posterior minus prior).",
  "Behave (msg 2) is willingness to act in line with the second message, recoded analogously."
)

custom.coef.map <- list(
  "inconsistent" = "Inconsistent",
  "trusted" = "Scientific (sender identity)",
  "science" = "Science (deemed optimum can change)",
  "inconsistent:trusted" = "Inconsistent $\\times$ Scientific",
  "inconsistent:science" = "Inconsistent $\\times$ Science",
  "trusted:science" = "Sender: scientific $\\times$ Science",
  "inconsistent:trusted:science" = "Inconsistent $\\times$ Scientific $\\times$ Science"
)

iv_coef_map <- list(
  "treatment_measurement" = "Perceived inconsistency"
)

write_texreg <- function(models, file, caption, label,
                         coef_map = custom.coef.map,
                         names = mod_names,
                         note = table_note_outcomes) {
  tab <- texreg::texreg(
    models,
    include.ci = FALSE,
    custom.model.names = names,
    caption = caption,
    stars = c(0.01, 0.05, 0.1),
    custom.coef.map = coef_map,
    label = label,
    custom.note = note
  )
  write(tab, file = file)
  tab
}

show_htmlreg <- function(models, caption, names = mod_names,
                         coef_map = custom.coef.map, note = NULL, ...) {
  extra <- list(...)
  args <- c(
    list(
      l = models,
      include.ci = FALSE,
      custom.model.names = names,
      caption = caption,
      stars = c(0.01, 0.05, 0.1),
      doctype = FALSE
    ),
    extra
  )
  if (!is.null(coef_map)) args$custom.coef.map <- coef_map
  if (!is.null(note)) args$custom.note <- note
  do.call(texreg::htmlreg, args)
}

prior_group <- function(x) {
  cut(
    x,
    breaks = c(-Inf, prior_low, prior_high, Inf),
    labels = c("mixing unsafe", "uncertain", "mixing safe"),
    right = TRUE
  )
}

science_lab <- function(x) {
  if_else(
    x == 1,
    "science video (deemed optimum can change)",
    "no science video"
  )
}
```

# 3. Data import

```{r}
#| label: import-vignettes

label <- read_dta(vignette_file) |>
  mutate(vignr = as.numeric(vignr)) |>
  mutate(
    unsafe_time1 = as.numeric(info1 == 1 | info1 == 2),
    unsafe_time2 = as.numeric(info2 == 1 | info2 == 2),
    safe_time1 = as.numeric(info1 == 3 | info1 == 4),
    safe_time2 = as.numeric(info2 == 3 | info2 == 4),
    inconsistent = case_when(
      info1 <= 2 & info2 <= 2 ~ 0,
      info1 > 2 & info2 > 2 ~ 0,
      info1 <= 2 & info2 > 2 ~ 1,
      info1 > 2 & info2 <= 2 ~ 1,
      TRUE ~ NA_real_
    )
  )
```

```{r}
#| label: import-survey

thirdwave <-
  read_sav(survey_file) |>
  rename(
    vignr = c_0031,
    age = v_15,
    gender = v_16,
    state = v_23,
    vaccination_status = v_28,
    vaccine_type = v_372,
    vaccine_first = v_395,
    vaccine_second = v_399,
    covid_invection = v_41,
    trust_government = v_59,
    trust_experts = v_60,
    trust_state_gov = v_61,
    trust_media = v_62,
    trust_stiko = v_378,
    political_interest = v_64,
    party_id = v_69,
    prior_pfm = v_192,
    prior_vac_pfm = v_193,
    salience_vac = v_194,
    prior_mixed = v_374,
    credible = v_382,
    competent = v_383,
    correct = v_384,
    post_mixed = v_401,
    behav_mixed = v_425,
    incumbent_voting = v_327,
    treatment_measurement = v_426,
    manipulation_time1 = v_404,
    manipulation_time2 = v_405,
    manipulation_time3 = v_406,
    manipulation_consistency = v_402,
    manipulation_science = v_403
  ) |>
  mutate(
    belief_update = post_mixed - prior_mixed,
    belief_update_abs = abs(post_mixed - prior_mixed),
    vignr = recode(
      as.character(vignr),
      "49" = "1", "50" = "4", "51" = "9", "52" = "12",
      "53" = "13", "54" = "16", "55" = "21", "56" = "24",
      "57" = "25", "58" = "28", "59" = "33", "60" = "36",
      "61" = "37", "62" = "40", "63" = "45", "64" = "48"
    ),
    vignr = as.numeric(vignr)
  ) |>
  left_join(label, by = "vignr") |>
  mutate(
    # Original vignette coding: 0 = STIKO, 1 = government.
    # Flip so trusted = 1 is STIKO (high trust), matching Table 1 in the paper.
    sender_treat = case_when(
      sender_treat == 0 ~ 1,
      sender_treat == 1 ~ 0
    ),
    trusted = sender_treat,
    science = info_treat,
    types = case_when(
      unsafe_time1 == 1 & safe_time2 == 1 ~ "unsafe-safe",
      unsafe_time1 == 1 & unsafe_time2 == 1 ~ "unsafe-unsafe",
      safe_time1 == 1 & unsafe_time2 == 1 ~ "safe-unsafe",
      safe_time1 == 1 & safe_time2 == 1 ~ "safe-safe"
    ),
    convinced_of_message_2 = safe_time2 * post_mixed + (1 - safe_time2) * (10 - post_mixed),
    behave_as_message_2 = safe_time2 * behav_mixed + (1 - safe_time2) * (10 - behav_mixed)
  )

# 0/1 treatment means: demeaning helpers subtract these, they do not overwrite thirdwave.
treatment_means <- thirdwave |>
  summarise(
    across(
      all_of(c(treatment_vars, "safe_time2")),
      \(x) mean(as.numeric(x), na.rm = TRUE)
    ),
    n = n()
  )
treatment_means
```

# 4. Paper

## Table 1. Events, likelihoods {#tbl-likelihoods}

Hardcoded in the paper (not estimated from the survey). Displayed here so the HTML matches the manuscript.

```{r}
#| label: paper-table-1

knitr::kable(
  tibble::tribble(
    ~Event, ~Prior, ~`Pr(s1=1, s2=1)`, ~`Pr(s1=1, s2=0)`,
    "(0, 0, 0)", "$p_{00}(1-q)$", "$(1-r)^2$", "$r(1-r)$",
    "(0, 1, 0)", "$p_{01}(1-q)$", "$r(1-r)$", "$(1-r)^2$",
    "(1, 0, 0)", "$p_{10}(1-q)$", "$r(1-r)$", "$r^2$",
    "(1, 1, 0)", "$p_{11}(1-q)$", "$r^2$", "$r(1-r)$",
    "(0, 0, 1)", "$p_{00}q$", "$0$", "$0$",
    "(0, 1, 1)", "$p_{01}q$", "$0$", "$0$",
    "(1, 0, 1)", "$p_{10}q$", "$0$", "$1$",
    "(1, 1, 1)", "$p_{11}q$", "$1$", "$0$"
  ),
  caption = "Table 1. Events, likelihoods.",
  escape = FALSE
)
```

## Figure 1. Theoretical predictions for policy support {#fig-policy}

Produced by `theory.qmd` (`policy.pdf`). $\alpha$ is the probability that evidence continues to deem the same policy optimal; underlying optimality does not change.

```{r}
#| label: paper-figure-1
#| fig-cap: "Figure 1. Theoretical predictions for support for policy 1 given messaging history, prior trust in the sender (q), prior beliefs of changing evidence (α), and prior beliefs about the issue p."

knitr::include_graphics(file.path(fig_dir, "policy.pdf"))
```

## Figure 2. Theoretical predictions for credibility {#fig-credibility}

Produced by `theory.qmd` (`credibility.pdf`).

```{r}
#| label: paper-figure-2
#| fig-cap: "Figure 2. Theoretical predictions for credibility beliefs conditional on messaging history, prior trust in the sender (q), prior beliefs of changing evidence (α), and prior beliefs about the issue p."

knitr::include_graphics(file.path(fig_dir, "credibility.pdf"))
```

## Figure 3. Public debate and prior attitudes {#fig-prior}

Google Trends is optional (API). The current paper figure is included so the replication HTML matches the manuscript. Uncomment the `gtrendsR` chunk to rebuild the top panel.

```{r}
#| label: paper-figure-3
#| fig-cap: "Figure 3. Descriptive Evidence: Public debate and prior attitudes towards vaccine mixing."

knitr::include_graphics(file.path(fig_dir, "figure_10.pdf"))
```

```{r}
#| label: paper-priors-histogram

prior_mixed_hist <- thirdwave |>
  ggplot(aes(prior_mixed)) +
  geom_histogram(binwidth = 1, alpha = 0.6) +
  xlab("Prior: how safe is mixing vaccines (0 unsafe, 10 safe)") +
  theme_bw(base_size = 14)

prior_mixed_hist
```

## Table 2. Experimental design {#tbl-example}

Hardcoded in the paper.

```{r}
#| label: paper-table-2

knitr::kable(
  tibble::tribble(
    ~Factor, ~Level,
    "$T_1$ Science updating ($\\alpha$)", "(0) No video; (1) Video, changing evidence is normal science",
    "$T_2$ Sender ($q$)", "(0) government; (1) scientific institution (STIKO)",
    "$T_3$ Message", "(1) safe-safe; (2) unsafe-unsafe; (3) unsafe-safe; (4) safe-unsafe",
    "$T_4$ Baseline (safe/unsafe)", "(0) $T_3 \\in \\{1,4\\}$; (1) $T_3 \\in \\{2,3\\}$",
    "$T_5$ Inconsistent message ($s$)", "(0) $T_3 \\in \\{1,2\\}$; (1) $T_3 \\in \\{3,4\\}$"
  ),
  caption = "Table 2. Experimental design: Factors and levels.",
  escape = FALSE
)
```

## Figure 4. Raw data patterns disaggregated by priors {#fig-raw}

```{r}
#| label: paper-figure-4
#| fig-cap: "Figure 4. Raw data patterns disaggregated by priors. Outcomes given experimental conditions."

summary_data <-
  thirdwave |>
  mutate(
    prior = prior_group(prior_mixed),
    science = info_treat,
    trust = sender_treat,
    Z = paste0(safe_time1, "/", safe_time2)
  ) |>
  transmute(
    safe_time1, safe_time2, science, trust, Z, prior,
    credible = as.numeric(credible),
    competent = as.numeric(competent),
    correct = as.numeric(correct),
    convinced = post_mixed,
    act = behav_mixed
  ) |>
  pivot_longer(
    c(credible, competent, correct, convinced, act),
    names_to = "Y",
    values_to = "val"
  ) |>
  group_by(safe_time1, safe_time2, science, trust, Z, Y, prior) |>
  summarise(
    n = sum(!is.na(val)),
    mean = mean(val, na.rm = TRUE),
    sd = sd(val, na.rm = TRUE),
    se = sd / sqrt(n),
    tcrit = qt(0.975, df = pmax(n - 1, 1)),
    lwr = mean - tcrit * se,
    upr = mean + tcrit * se,
    .groups = "drop"
  ) |>
  mutate(
    trust_lab = if_else(trust == 1, "high-trust institution", "low-trust institution"),
    science_lab = science_lab(science),
    cond = paste(trust_lab, science_lab, sep = "\n"),
    cond = factor(
      cond,
      levels = c(
        paste("high-trust institution", science_lab(0), sep = "\n"),
        paste("high-trust institution", science_lab(1), sep = "\n"),
        paste("low-trust institution", science_lab(0), sep = "\n"),
        paste("low-trust institution", science_lab(1), sep = "\n")
      )
    ),
    Z = recode(
      Z,
      "0/0" = "unsafe-unsafe",
      "0/1" = "unsafe-safe",
      "1/0" = "safe-unsafe",
      "1/1" = "safe-safe"
    ),
    Z = factor(Z, c("unsafe-unsafe", "unsafe-safe", "safe-unsafe", "safe-safe"))
  )

all_row <- summary_data |>
  group_by(safe_time1, safe_time2, Z, Y, prior) |>
  summarise(
    N = sum(n),
    mu = sum(mean * n) / N,
    var_num = sum((n - 1) * sd^2 + n * (mean - mu)^2),
    sd = sqrt(var_num / pmax(N - 1, 1)),
    se = sd / sqrt(N),
    tcrit = qt(0.975, df = pmax(N - 1, 1)),
    lwr = mu - tcrit * se,
    upr = mu + tcrit * se,
    .groups = "drop"
  ) |>
  transmute(
    safe_time1, safe_time2, Z, Y, prior,
    n = N, mean = mu, sd, se, tcrit, lwr, upr,
    trust_lab = NA_character_, science_lab = NA_character_,
    cond = factor("All conditions", levels = c("All conditions", levels(summary_data$cond)))
  )

summary_data <- bind_rows(
  all_row,
  summary_data |> mutate(cond = fct_relevel(cond, "All conditions"))
) |>
  mutate(
    Y = factor(
      Y,
      c("competent", "credible", "correct", "convinced", "act"),
      c("competent", "credible", "correct", "belief\n(trusts mixing)", "behavior\n(would mix)")
    )
  )

raw_patterns_disagg <- ggplot(summary_data, aes(x = Z, y = mean, color = prior)) +
  facet_grid(cond ~ Y, labeller = label_value) +
  geom_point() +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0.15) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    legend.position = "bottom"
  ) +
  labs(
    x = "Policy 1 / Policy 2",
    y = "",
    color = "Prior on mixing",
    caption = "Belief/behavior panels are support for mixing, not agreement with message 2."
  )

raw_patterns_disagg
ggsave(file.path(fig_dir, "raw_disagg.pdf"), raw_patterns_disagg, width = 8, height = 8)
```

## Table 3. Fully saturated model {#tbl-saturated}

Estimand is unchanged. Labels distinguish Belief/Behave (agreement with message 2) from belief updating.

```{r}
#| label: paper-table-3

saturated <- fit_saturated_list(thirdwave)

tab_sat <- write_texreg(
  saturated,
  file = file.path(fig_dir, "tab_1_full.tex"),
  caption = "Fully saturated model",
  label = "table:saturated"
)
```

```{r}
#| label: paper-table-3-html
#| results: asis

texreg::htmlreg(
  saturated,
  include.ci = FALSE,
  custom.model.names = mod_names,
  caption = "Table 3. Fully saturated model. Belief (msg 2) and Behave (msg 2) are recoded agreement with the second recommendation, not belief updating. Treatments demeaned (Lin 2013).",
  stars = c(0.01, 0.05, 0.1),
  custom.coef.map = custom.coef.map,
  doctype = FALSE
)
```

## Figure 5. ITT and LATE {#fig-itt}

Assignment (`inconsistent`, 0/1) instruments perceived inconsistency (`treatment_measurement`).

```{r}
#| label: paper-figure-5
#| fig-cap: "Figure 5. Intent-to-treat (ITT) and local average treatment (LATE) effect."

models_basic <- lapply(outcomes, function(y) {
  lm_robust(as.formula(paste(y, "~ inconsistent")), data = thirdwave)
})
names(models_basic) <- outcomes

subfigure_1_itt <- lapply(models_basic, tidy) |>
  bind_rows(.id = "outcome") |>
  mutate(Model = "ITT") |>
  filter(term != "(Intercept)") |>
  mutate(outcome = factor(outcome, outcomes, outcome_labels)) |>
  select(-any_of("df"))

models_iv <- lapply(outcomes, function(y) {
  iv_robust(
    as.formula(paste(y, "~ treatment_measurement | inconsistent")),
    data = thirdwave
  )
})
names(models_iv) <- outcomes

subfigure_1_iv <- lapply(models_iv, tidy) |>
  bind_rows(.id = "outcome") |>
  mutate(Model = "LATE") |>
  filter(term != "(Intercept)") |>
  mutate(outcome = factor(outcome, outcomes, outcome_labels)) |>
  select(-any_of("df"))

data_figure5 <- bind_rows(subfigure_1_itt, subfigure_1_iv)

figure_5 <- data_figure5 |>
  ggplot(aes(estimate, outcome, color = Model, shape = Model)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.3),
    width = 0.1
  ) +
  geom_vline(xintercept = 0, linetype = "longdash") +
  xlab("Effect of Inconsistent Information") +
  ylab("Outcome") +
  labs(
    caption = "Belief (msg 2) and Behave (msg 2) are recoded agreement with the second recommendation."
  ) +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank(), text = element_text(size = 16)) +
  coord_flip()

figure_5
ggsave(file.path(fig_dir, "figure_1.pdf"), figure_5, width = 8, height = 5)
ggsave(file.path(fig_dir, "figure_5.pdf"), figure_5, width = 8, height = 5)
```

```{r}
#| label: paper-figure-5-itt-html
#| results: asis

show_htmlreg(
  models_basic,
  caption = "ITT companion to Figure 5. Inconsistency assignment. Same outcomes as Table 3."
)
```

```{r}
#| label: paper-figure-5-late-html
#| results: asis

show_htmlreg(
  models_iv,
  caption = "LATE/IV companion to Figure 5. Perceived inconsistency instrumented by assignment. Same outcomes as Table 3.",
  coef_map = iv_coef_map
)
```

## Figure 6. Inconsistency conditional on science video {#fig-science-information}

Conditional coefficients of inconsistency at no-video and video, from the same demeaned saturated specification as Table 3. Figure 6 plots only Credible, Competent, and Correct (not Belief/Behave). Vertical error bars (`geom_errorbar` with ymin/ymax). The paper text on this figure concerns the *interaction* (whether the video weakens the inconsistency penalty), not the main effect of the video.

```{r}
#| label: paper-figure-6
#| fig-cap: "Figure 6. Effect of Inconsistent Information conditional on the receipt of scientific information intervention."

mean_science <- mean(as.numeric(thirdwave$science), na.rm = TRUE)
fig6_idx <- 1:3
fig6_order <- c("Competent", "Correct", "Credible")
fig6_xlab <- c("Competence", "Correctness", "Credibility")

science_me <- map_dfr(fig6_idx, function(i) {
  fit <- saturated[[i]]
  b <- coef(fit)
  V <- vcov(fit)
  inc <- "inconsistent"
  int <- "inconsistent:science"
  tibble(science_raw = c(0, 1), outcome = outcome_labels[i]) |>
    mutate(
      s_d = science_raw - mean_science,
      estimate = b[[inc]] + b[[int]] * s_d,
      se = sqrt(
        V[inc, inc] + (s_d^2) * V[int, int] + 2 * s_d * V[inc, int]
      ),
      conf.low = estimate - 1.96 * se,
      conf.high = estimate + 1.96 * se,
      science = factor(science_raw, levels = c(0, 1), labels = c("0", "1"))
    )
}) |>
  mutate(
    outcome = factor(outcome, fig6_order, fig6_xlab)
  )

figure_6 <- science_me |>
  ggplot(aes(outcome, estimate, color = science, shape = science)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  geom_point(position = position_dodge(width = 0.4), size = 3) +
  geom_errorbar(
    aes(ymin = conf.low, ymax = conf.high),
    position = position_dodge(width = 0.4),
    width = 0.15
  ) +
  xlab("Outcome") +
  ylab("Effect of Inconsistency Treatment") +
  labs(
    color = "Science Information Treatment",
    shape = "Science Information Treatment",
    caption = "Conditional coefficients of inconsistency given the science-video arm. Table 3 demeaned specification. 95% intervals."
  ) +
  theme_bw() +
  theme(legend.position = "bottom")

figure_6
ggsave(file.path(fig_dir, "figure_3_new.pdf"), figure_6, width = 8, height = 5)
ggsave(file.path(fig_dir, "figure_6.pdf"), figure_6, width = 8, height = 5)
```

# 5. SI

## Table A.1. Statistical models (OxCGRT) {#tbl-coefficients-policy}

Country-day OxCGRT (2022-07 legacy snapshot) merged with Pulejo and Querubin (2021) election data. Table A.1 is the Government Response Index specification, N = 65. Appendix prose describes the Containment Health Index; the printed coefficients match GRI.

```{r}
#| label: si-oxcgrt-data

oxcgrt_raw <- if (nzchar(oxcgrt_csv) && file.exists(oxcgrt_csv)) {
  read.csv(oxcgrt_csv)
} else {
  read.csv(oxcgrt_url)
}
oxcgrt_raw <- transform(oxcgrt_raw, Date = as.Date(as.character(Date), "%Y%m%d"))

policy_variables <- c(
  "ContainmentHealthIndex",
  "StringencyIndex",
  "GovernmentResponseIndex",
  "C1_School.closing",
  "C2_Workplace.closing",
  "C3_Cancel.public.events",
  "C4_Restrictions.on.gatherings",
  "C5_Close.public.transport",
  "C6_Stay.at.home.requirements",
  "C7_Restrictions.on.internal.movement",
  "C8_International.travel.controls",
  "H1_Public.information.campaigns",
  "H2_Testing.policy",
  "H3_Contact.tracing",
  "H6_Facial.Coverings",
  "H7_Vaccination.policy",
  "H8_Protection.of.elderly.people"
)

oxcgrt_daily <- oxcgrt_raw |>
  subset(Date < as.Date("2020-05-29")) |>
  dplyr::filter(Jurisdiction == "NAT_TOTAL") |>
  dplyr::select(CountryCode, CountryName, Date, dplyr::any_of(policy_variables))

election <- read_dta(election_file) |>
  dplyr::select(
    countryname,
    timetocase1,
    maxconsecutiveterms,
    termlength,
    canrun,
    electionproximity_yrs,
    electionproximity_yrs_canrun,
    Z_bci_bci,
    Z_cspf_sfi
  )

oxcgrt_merged <- merge(
  oxcgrt_daily,
  election,
  by.x = "CountryName",
  by.y = "countryname"
)

policy_present <- intersect(policy_variables, names(oxcgrt_merged))

oxcgrt <- oxcgrt_merged |>
  group_by(CountryName) |>
  summarize(
    across(
      all_of(policy_present),
      .fns = list(
        sd = \(x) sd(x, na.rm = TRUE),
        fluctuation = \(x) sd(diff(x), na.rm = TRUE),
        changes = \(x) sum(diff(x) != 0, na.rm = TRUE),
        reversals1 = \(x) sum(diff(sign(diff(x))) != 0, na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) |>
  merge(election, by.x = "CountryName", by.y = "countryname")

c(n_countries = nrow(oxcgrt))
```

```{r}
#| label: si-table-a1

a1_rhs <- "canrun + electionproximity_yrs + electionproximity_yrs_canrun"
a1_models <- list(
  sd = lm_robust(as.formula(paste("GovernmentResponseIndex_sd ~", a1_rhs)), data = oxcgrt),
  fluctuations = lm_robust(
    as.formula(paste("GovernmentResponseIndex_fluctuation ~", a1_rhs)),
    data = oxcgrt
  ),
  changes = lm_robust(
    as.formula(paste("GovernmentResponseIndex_changes ~", a1_rhs)),
    data = oxcgrt
  ),
  reversals = lm_robust(
    as.formula(paste("GovernmentResponseIndex_reversals1 ~", a1_rhs)),
    data = oxcgrt
  )
)
a1_names <- c("sd", "fluctuations", "changes", "reversals")
a1_coef_map <- list(
  "canrun" = "Can Run",
  "electionproximity_yrs" = "Electoral Proximity",
  "electionproximity_yrs_canrun" = "Proximity $\\times$ Can Run"
)

tab_a1 <- texreg::texreg(
  a1_models,
  include.ci = FALSE,
  omit.coef = "(Intercept)",
  custom.model.names = a1_names,
  custom.coef.map = a1_coef_map,
  caption = "Statistical models",
  label = "table:coefficients:policy",
  stars = c(0.001, 0.01, 0.05, 0.1)
)
write(tab_a1, file = file.path(fig_dir, "tab_a1_policy.tex"))
```

```{r}
#| label: si-table-a1-html
#| results: asis

show_htmlreg(
  a1_models,
  caption = "Table A.1. Statistical models. Government Response Index; N = 65. Can Run, Electoral Proximity, and their interaction.",
  names = a1_names,
  coef_map = list(
    "canrun" = "Can Run",
    "electionproximity_yrs" = "Electoral Proximity",
    "electionproximity_yrs_canrun" = "Proximity × Can Run"
  ),
  omit.coef = "(Intercept)"
)
```

## Figure A.1. The Effect of Elections on Policy Changes {#fig-policy-updating}

Conditional coefficients on proximity × can-run for the CHI component indicators.

```{r}
#| label: si-figure-a1
#| fig-cap: "Figure A.1. The Effect of Elections on Policy Changes."

policy_labels <- c(
  "C1_School.closing" = "School closing",
  "C2_Workplace.closing" = "Workplace closing",
  "C3_Cancel.public.events" = "Public events",
  "C4_Restrictions.on.gatherings" = "Restrictions gatherings",
  "C5_Close.public.transport" = "Public transport",
  "C6_Stay.at.home.requirements" = "Stay home",
  "C7_Restrictions.on.internal.movement" = "Restrictions movement",
  "C8_International.travel.controls" = "International travel",
  "H1_Public.information.campaigns" = "Information campaigns",
  "H2_Testing.policy" = "Testing policy",
  "H3_Contact.tracing" = "Contact tracing",
  "H6_Facial.Coverings" = "Facial coverings",
  "H7_Vaccination.policy" = "Vaccination policy",
  "H8_Protection.of.elderly.people" = "Protection elderly"
)

indicator_vars <- setdiff(
  policy_present,
  c("ContainmentHealthIndex", "StringencyIndex", "GovernmentResponseIndex")
)

a1_fig_dat <- map_dfr(indicator_vars, function(variable) {
  map_dfr(c("_sd", "_fluctuation", "_changes", "_reversals1"), function(measure) {
    outcome <- paste0(variable, measure)
    if (!outcome %in% names(oxcgrt)) {
      return(NULL)
    }
    fit <- lm(as.formula(paste(outcome, "~", a1_rhs)), data = oxcgrt)
    sm <- summary(fit)$coef
    tibble(
      outcome = outcome,
      coef_value = unname(sm["electionproximity_yrs_canrun", "Estimate"]),
      std_error = unname(sm["electionproximity_yrs_canrun", "Std. Error"]),
      group = measure
    )
  })
})

fig_pol_updating <- a1_fig_dat |>
  mutate(
    policy = case_when(
      substr(outcome, 1, 1) == "C" ~ "containment and closure policies",
      substr(outcome, 1, 1) == "H" ~ "health system policies",
      TRUE ~ NA_character_
    ),
    outcome = stringr::str_remove_all(outcome, "_sd|_fluctuation|_changes|_reversals1"),
    group = recode(
      group,
      "_sd" = "Standard Deviation",
      "_fluctuation" = "Fluctuations",
      "_changes" = "Changes",
      "_reversals1" = "Reversals 1"
    )
  ) |>
  ggplot(aes(
    x = factor(outcome, levels = names(policy_labels)),
    y = coef_value,
    color = policy
  )) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_point() +
  geom_errorbar(
    aes(ymin = coef_value - 1.96 * std_error, ymax = coef_value + 1.96 * std_error),
    width = 0.2
  ) +
  labs(x = "Policy Measure", y = "Proximity X Can Run") +
  facet_wrap(~group, scales = "free_y", ncol = 2) +
  scale_x_discrete(labels = policy_labels) +
  theme_bw() +
  theme(
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    legend.position = "bottom"
  )

fig_pol_updating
ggsave(file.path(fig_dir, "fig_pol_updating.pdf"), fig_pol_updating, width = 8, height = 5)
```

## Figure C.1. Survey instrument (introduction and treatments) {#fig-c1}

Static Overleaf screenshot. Not generated by this qmd. Introduction, treatment messages, and manipulation checks (`Screenshot_2021-09-08 Umfrage(1–5).png`).

## Figure C.2. Survey instrument (timing) {#fig-c2}

Static Overleaf screenshot. Not generated by this qmd. Timing questions (`Screenshot_2021-09-08 Umfrage(6–8).png`).

## Table D.1. Summary statistics {#tbl-d1}

```{r}
#| label: si-summary-stats

summ_vars <- thirdwave |>
  select(
    age, gender, vaccination_status, vaccine_type, covid_invection,
    trust_government, trust_experts, trust_state_gov, trust_media, trust_stiko,
    political_interest, party_id, prior_pfm, prior_vac_pfm, salience_vac,
    credible, competent, correct, prior_mixed, post_mixed, behav_mixed,
    incumbent_voting, treatment_measurement
  )

summary_table <- summ_vars |>
  mutate(across(everything(), as.numeric)) |>
  summarise(across(
    everything(),
    list(
      N = \(x) sum(!is.na(x)),
      Mean = \(x) mean(x, na.rm = TRUE),
      `Std. Dev.` = \(x) sd(x, na.rm = TRUE),
      Min = \(x) min(x, na.rm = TRUE),
      `Pctl. 25` = \(x) quantile(x, 0.25, na.rm = TRUE),
      `Pctl. 75` = \(x) quantile(x, 0.75, na.rm = TRUE),
      Max = \(x) max(x, na.rm = TRUE)
    ),
    .names = "{.col}__{.fn}"
  )) |>
  pivot_longer(everything(), names_to = c("Variable", "Statistic"), names_sep = "__") |>
  pivot_wider(names_from = "Statistic", values_from = "value") |>
  arrange(Variable)

knitr::kable(
  summary_table,
  digits = 2,
  col.names = c("Variable", "N", "Mean", "Std. Dev.", "Min", "Pctl. 25", "Pctl. 75", "Max"),
  caption = "Table D.1. Summary Statistics"
) |>
  kableExtra::kable_styling(full_width = FALSE)

writeLines(
  knitr::kable(summary_table, format = "latex", digits = 2, booktabs = TRUE),
  file.path(fig_dir, "tab_summary_stats.tex")
)
```

## Figure D.1. Prior and posterior beliefs {#fig-priors}

```{r}
#| label: si-figure-d1
#| fig-cap: "Figure D.1. Prior and Posterior Beliefs, Belief Updating"

prior <- tibble(value = thirdwave$prior_mixed, Belief = "prior")
post <- tibble(value = thirdwave$post_mixed, Belief = "posterior")

prior_posterior <- bind_rows(prior, post) |>
  ggplot(aes(value, fill = Belief)) +
  geom_density(alpha = 0.2) +
  xlab("Beliefs about vaccine mixing") +
  theme_bw()

belief_update_plot <- thirdwave |>
  ggplot(aes(belief_update)) +
  geom_histogram(binwidth = 1, alpha = 0.6) +
  xlab("Belief updating (posterior − prior)") +
  theme_bw()

belief_update_abs_plot <- thirdwave |>
  ggplot(aes(belief_update_abs)) +
  geom_histogram(binwidth = 1, alpha = 0.6) +
  xlab("Absolute belief updating") +
  theme_bw()

fig_13 <- grid.arrange(prior_posterior, belief_update_plot, belief_update_abs_plot, ncol = 3)
ggsave(file.path(fig_dir, "figure_13.pdf"), fig_13, width = 10, height = 4)
```

## Table E.1. Science-video manipulation check {#tbl-e1}

Science video: share who say contradicting studies are compatible with scientific progress.

```{r}
#| label: si-table-e1

man_science <- lm_robust(
  I(manipulation_science == 1) ~ science,
  data = thirdwave
)
summary(man_science)

tab_man_science <- texreg::texreg(
  man_science,
  include.ci = FALSE,
  caption = "Science-video manipulation check",
  label = "tab:man_science",
  stars = c(0.01, 0.05, 0.1),
  custom.coef.map = list("(Intercept)" = "Constant", "science" = "Science video")
)
write(tab_man_science, file = file.path(fig_dir, "tab_man_science.tex"))
```

```{r}
#| label: si-table-e1-html
#| results: asis

show_htmlreg(
  man_science,
  caption = "Table E.1. Science-video manipulation check (Inconsistencies in Science).",
  names = "Inconsistencies in Science",
  coef_map = list("(Intercept)" = "Constant", "science" = "Science video")
)
```

## Table E.2. Treatment compliance (first stage) {#tbl-treatment-compliance}

Perceived inconsistency (first stage for the IV).

```{r}
#| label: si-table-e2

man_iv <- lm_robust(treatment_measurement ~ inconsistent, data = thirdwave)
summary(man_iv)

tab_man_iv <- texreg::texreg(
  man_iv,
  include.ci = FALSE,
  caption = "Treatment compliance (perceived inconsistency)",
  label = "TreatmentCompliance",
  stars = c(0.01, 0.05, 0.1),
  custom.coef.map = list(
    "(Intercept)" = "Constant",
    "inconsistent" = "Instrument (inconsistent information)"
  )
)
write(tab_man_iv, file = file.path(fig_dir, "tab_treatment_compliance.tex"))
```

```{r}
#| label: si-table-e2-html
#| results: asis

show_htmlreg(
  man_iv,
  caption = "Table E.2. Treatment Compliance.",
  names = "Treatment Measurement",
  coef_map = list(
    "(Intercept)" = "Constant",
    "inconsistent" = "Instrument (inconsistent information)"
  )
)
```

## Table E.3. Manipulation perceived timing {#tbl-coefficients}

Perceived timing of recommendations.

```{r}
#| label: si-table-e3

man_t1_safe <- lm_robust(as.numeric(manipulation_time1) ~ safe_time1, data = thirdwave)
man_t1_unsafe <- lm_robust(as.numeric(manipulation_time1) ~ unsafe_time1, data = thirdwave)
man_t2_safe <- lm_robust(as.numeric(manipulation_time2) ~ safe_time2, data = thirdwave)
man_t2_unsafe <- lm_robust(as.numeric(manipulation_time2) ~ unsafe_time2, data = thirdwave)

tab_man1 <- texreg::texreg(
  list(man_t1_safe, man_t1_unsafe, man_t2_safe, man_t2_unsafe),
  include.ci = FALSE,
  custom.model.names = c("manipulation t1", "manipulation t1", "manipulation t2", "manipulation t2"),
  caption = "Manipulation perceived timing",
  label = "table:coefficients",
  stars = c(0.001, 0.01, 0.05),
  custom.coef.map = list(
    "safe_time1" = "safe\\_time1",
    "unsafe_time1" = "unsafe\\_time1",
    "safe_time2" = "safe\\_time2",
    "unsafe_time2" = "unsafe\\_time2"
  )
)
write(tab_man1, file = file.path(fig_dir, "tab_man1.tex"))
```

```{r}
#| label: si-table-e3-html
#| results: asis

show_htmlreg(
  list(man_t1_safe, man_t1_unsafe, man_t2_safe, man_t2_unsafe),
  caption = "Table E.3. Manipulation perceived timing.",
  names = c("manipulation t1", "manipulation t1", "manipulation t2", "manipulation t2"),
  coef_map = list(
    "safe_time1" = "safe_time1",
    "unsafe_time1" = "unsafe_time1",
    "safe_time2" = "safe_time2",
    "unsafe_time2" = "unsafe_time2"
  )
)
```

## Table F.1. Inquiry reconciliation {#tbl-inquiry-reconciliation}

## Table F.2. Parameter mapping {#tbl-parameter-mapping}

## Table F.3. Answer strategy {#tbl-answer-strategy}

Hardcoded in `appendix.tex` (inquiry reconciliation, parameter mapping, answer strategy). Not generated from the survey file.

## Table G.1. Ordering: first message against mixing {#tbl-saturated-0}

## Table G.2. Ordering: first message for mixing {#tbl-saturated-1}

Filters use the stored 0/1 `safe_time1`, not a demeaned copy.

```{r}
#| label: si-order-tables

sat_0 <- fit_saturated_list(
  filter(thirdwave, safe_time1 == 0),
  rhs = "inconsistent * trusted * science"
)
sat_1 <- fit_saturated_list(
  filter(thirdwave, safe_time1 == 1),
  rhs = "inconsistent * trusted * science"
)

tab_sat_0 <- write_texreg(
  sat_0,
  file = file.path(fig_dir, "tab_1_full_0.tex"),
  caption = "Fully saturated model | first message against mixing",
  label = "table:saturated_0"
)
tab_sat_1 <- write_texreg(
  sat_1,
  file = file.path(fig_dir, "tab_1_full_1.tex"),
  caption = "Fully saturated model | first message supports mixing",
  label = "table:saturated_1"
)
```

```{r}
#| label: si-order-html
#| results: asis

texreg::htmlreg(
  sat_0,
  include.ci = FALSE,
  custom.model.names = mod_names,
  caption = "Table G.1. Fully saturated model | first message against mixing",
  stars = c(0.01, 0.05, 0.1),
  custom.coef.map = custom.coef.map,
  doctype = FALSE
)
texreg::htmlreg(
  sat_1,
  include.ci = FALSE,
  custom.model.names = mod_names,
  caption = "Table G.2. Fully saturated model | first message supports mixing",
  stars = c(0.01, 0.05, 0.1),
  custom.coef.map = custom.coef.map,
  doctype = FALSE
)
```

## Table G.3. Saturated model accounting for priors {#tbl-saturated-priors}

```{r}
#| label: si-table-g3

thirdwave_prior <- thirdwave |>
  mutate(prior = prior_mixed - mean(prior_mixed, na.rm = TRUE))

sat_priors <- lapply(outcomes, function(y) {
  d <- with_demeaned_treatments(thirdwave_prior, c(treatment_vars, "prior"))
  lm_robust(
    as.formula(paste(y, "~ inconsistent * trusted * science * prior * safe_time1")),
    data = d
  )
})

tab_sat_priors <- write_texreg(
  sat_priors,
  file = file.path(fig_dir, "tab_1_full_priors.tex"),
  caption = "Fully saturated model | accounting for priors",
  label = "table:saturated_priors"
)

prior_interactions <- list(
  "inconsistent:trusted" = "Inconsistent $\\times$ Sender: scientific",
  "inconsistent:science" = "Inconsistent $\\times$ Science",
  "prior" = "Priors",
  "inconsistent:prior" = "Inconsistent $\\times$ Priors",
  "trusted:prior" = "Sender: scientific $\\times$ Priors",
  "science:prior" = "Science (deemed optimum can change) $\\times$ Priors",
  "inconsistent:safe_time1" = "Inconsistent $\\times$ Initial safe",
  "prior:safe_time1" = "Initial safe $\\times$ Priors",
  "inconsistent:prior:safe_time1" = "Inconsistent $\\times$ Initial safe $\\times$ Priors"
)

tab_sat_prior_int <- write_texreg(
  sat_priors,
  file = file.path(fig_dir, "tab_1_full_priors_interactions.tex"),
  caption = "Fully saturated model | priors on mixing and interactions with priors",
  label = "table:saturated_priors_interactions",
  coef_map = prior_interactions
)
```

```{r}
#| label: si-table-g3-html
#| results: asis

show_htmlreg(
  sat_priors,
  caption = "Table G.3. Fully saturated model | accounting for priors"
)
```

## Table G.4. Priors and interactions {#tbl-saturated-priors-interactions}

```{r}
#| label: si-table-g4-html
#| results: asis

show_htmlreg(
  sat_priors,
  caption = "Table G.4. Fully saturated model | priors on mixing and interactions with priors",
  coef_map = prior_interactions
)
```

## Figure G.1. Effect of information conditional on prior beliefs {#fig-cate-priors}

Twelve panels: Inconsistent / Safe / Unsafe × credibility, competence, correctness, posterior. Each panel is OLS `y ~ prior_mixed * treat` plotted with `interplot` (histogram of priors). Treatments stay 0/1; Lin demeaning is not used. `safe` and `unsafe` are defined from `info1`/`info2` (R parses `&` before `|`).

```{r}
#| label: si-figure-g1
#| fig-cap: "Figure G.1. Effect of information conditional on prior beliefs about vaccine mixing."

cate_dat_g1 <- thirdwave |>
  mutate(
    unsafe = as.numeric(info1 == 1 | info1 == 2 & info2 == 1 | info2 == 2),
    safe = as.numeric(info1 == 3 | info1 == 4 & info2 == 3 | info2 == 4)
  )

cate_panel <- function(data, y, treat, ylab, title) {
  m <- lm(as.formula(paste(y, "~ prior_mixed *", treat)), data = data)
  interplot::interplot(
    m = m,
    var1 = treat,
    var2 = "prior_mixed",
    hist = TRUE,
    adjCI = FALSE
  ) +
    geom_hline(
      yintercept = 0,
      linetype = "longdash",
      linewidth = 0.35,
      colour = "#B55555"
    ) +
    ylab(ylab) +
    xlab("Prior Beliefs Vaccine Mixing") +
    ggtitle(title) +
    theme_bw()
}

M1_plot <- cate_panel(cate_dat_g1, "credible", "inconsistent", "Treatment effect on sender credibility", "Inconsistent Information")
M2_plot <- cate_panel(cate_dat_g1, "credible", "safe", "Treatment effect on sender credibility", "Safe Information")
M3_plot <- cate_panel(cate_dat_g1, "credible", "unsafe", "Treatment effect on sender credibility", "Unsafe Information")
M4_plot <- cate_panel(cate_dat_g1, "competent", "inconsistent", "Treatment effect on sender competence", "Inconsistent Information")
M5_plot <- cate_panel(cate_dat_g1, "competent", "safe", "Treatment effect on sender competence", "Safe Information")
M6_plot <- cate_panel(cate_dat_g1, "competent", "unsafe", "Treatment effect on sender competence", "Unsafe Information")
M7_plot <- cate_panel(cate_dat_g1, "correct", "inconsistent", "Treatment effect information correct", "Inconsistent Information")
M8_plot <- cate_panel(cate_dat_g1, "correct", "safe", "Treatment effect information correct", "Safe Information")
M9_plot <- cate_panel(cate_dat_g1, "correct", "unsafe", "Treatment effect information correct", "Unsafe Information")
M7a_plot <- cate_panel(cate_dat_g1, "post_mixed", "inconsistent", "Posterior Beliefs", "Inconsistent Information")
M8a_plot <- cate_panel(cate_dat_g1, "post_mixed", "safe", "Posterior Beliefs", "Safe Information")
M9a_plot <- cate_panel(cate_dat_g1, "post_mixed", "unsafe", "Posterior Beliefs", "Unsafe Information")

fig_1 <- grid.arrange(
  M1_plot, M2_plot, M3_plot,
  M4_plot, M5_plot, M6_plot,
  M7_plot, M8_plot, M9_plot,
  M7a_plot, M8a_plot, M9a_plot,
  ncol = 3
)
ggsave(file.path(fig_dir, "fig_1.pdf"), fig_1, width = 10, height = 9)
```

## Table G.5. High priors {#tbl-saturated-high-priors}

## Table G.6. Medium priors {#tbl-saturated-med-priors}

## Table G.7. Low priors {#tbl-saturated-low-priors}

Cuts: low `< 3.3`, medium `(3.3, 6.6)`, high `> 6.6`. The previous high-priors table used `< 6.6` (low and medium stacked). Demeaning is within subgroup.

```{r}
#| label: si-prior-subgroups

dat_low <- filter(thirdwave, prior_mixed < prior_low)
dat_med <- filter(thirdwave, prior_mixed > prior_low & prior_mixed < prior_high)
dat_high <- filter(thirdwave, prior_mixed > prior_high)

c(
  low = nrow(dat_low),
  med = nrow(dat_med),
  high = nrow(dat_high),
  excluded_at_cuts = nrow(thirdwave) - nrow(dat_low) - nrow(dat_med) - nrow(dat_high)
)

sat_low <- fit_saturated_list(dat_low)
sat_med <- fit_saturated_list(dat_med)
sat_high <- fit_saturated_list(dat_high)

tab_sat_low <- write_texreg(
  sat_low,
  file = file.path(fig_dir, "tab_1_low_priors.tex"),
  caption = "Fully saturated model, subjects with low priors",
  label = "tab:saturated_low_priors"
)
tab_sat_med <- write_texreg(
  sat_med,
  file = file.path(fig_dir, "tab_1_med_priors.tex"),
  caption = "Fully saturated model, subjects with middling priors",
  label = "tab:saturated_med_priors"
)
tab_sat_high <- write_texreg(
  sat_high,
  file = file.path(fig_dir, "tab_1_high_priors.tex"),
  caption = "Fully saturated model, subjects with high priors",
  label = "tab:saturated_high_priors"
)
```

```{r}
#| label: si-tables-g5-g7-html
#| results: asis

show_htmlreg(sat_high, caption = "Table G.5. Fully saturated model, subjects with high priors")
show_htmlreg(sat_med, caption = "Table G.6. Fully saturated model, subjects with middling priors")
show_htmlreg(sat_low, caption = "Table G.7. Fully saturated model, subjects with low priors")
```

## Table G.8. ITT {#tbl-g8}

## Table G.9. IV {#tbl-g9}

Same 0/1 `inconsistent` as Figure 5. Outcomes match Table 3 (including recoded message-2 measures). Overleaf currently hardcodes `post_mixed` and `belief_update_abs` instead.

```{r}
#| label: si-tables-g8-g9

tab_itt <- texreg::texreg(
  models_basic,
  include.ci = FALSE,
  custom.model.names = mod_names,
  caption = "ITT: inconsistency assignment",
  stars = c(0.01, 0.05, 0.1),
  custom.note = table_note_outcomes
)
write(tab_itt, file = file.path(fig_dir, "tab_itt.tex"))

tab_iv <- texreg::texreg(
  models_iv,
  include.ci = FALSE,
  custom.model.names = mod_names,
  caption = "IV: perceived inconsistency instrumented by assignment",
  stars = c(0.01, 0.05, 0.1),
  custom.note = table_note_outcomes
)
write(tab_iv, file = file.path(fig_dir, "tab_iv.tex"))
```

```{r}
#| label: si-tables-g8-g9-html
#| results: asis

show_htmlreg(
  models_basic,
  caption = "Table G.8. ITT: inconsistency assignment. Same outcomes as Table 3."
)
show_htmlreg(
  models_iv,
  caption = "Table G.9. IV: perceived inconsistency instrumented by assignment. Same outcomes as Table 3.",
  coef_map = iv_coef_map
)
```

# 6. Additional

Objects not in the paper: four-type OLS by prior, pooled raw means, IV first-stage plot, unsaturated specification.

## Information types by prior

Predicted outcomes by four-level message type and prior (reference: unsafe-unsafe).

```{r}
#| label: additional-info-types-by-prior
#| fig-cap: "Additional (not in paper). Information types by prior, relative to unsafe-unsafe."

cate_dat <- thirdwave |>
  mutate(
    types = factor(types, c("unsafe-unsafe", "unsafe-safe", "safe-unsafe", "safe-safe"))
  )

cate_fits <- lapply(c("credible", "competent", "correct", "post_mixed"), function(y) {
  lm_robust(as.formula(paste(y, "~ types * prior_mixed")), data = cate_dat)
})
names(cate_fits) <- c("Credible", "Competent", "Correct", "Belief (mixing)")

grid_prior <- seq(0, 10, by = 0.5)
cate_plot_dat <- map_dfr(names(cate_fits), function(nm) {
  fit <- cate_fits[[nm]]
  b <- coef(fit)
  V <- vcov(fit)
  types_ok <- c("unsafe-safe", "safe-unsafe", "safe-safe")
  map_dfr(types_ok, function(tp) {
    tterm <- paste0("types", tp)
    pterm <- paste0("types", tp, ":prior_mixed")
    tibble(prior = grid_prior, outcome = nm, type = tp) |>
      mutate(
        estimate = b[[tterm]] + b[[pterm]] * prior,
        se = sqrt(V[tterm, tterm] + (prior^2) * V[pterm, pterm] + 2 * prior * V[tterm, pterm]),
        conf.low = estimate - 1.96 * se,
        conf.high = estimate + 1.96 * se
      )
  })
})

fig_types_by_prior <- cate_plot_dat |>
  ggplot(aes(prior, estimate, color = type, fill = type)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  geom_line() +
  facet_wrap(~outcome, scales = "free_y") +
  xlab("Prior: mixing is unsafe (0) to safe (10)") +
  ylab("Effect relative to unsafe-unsafe") +
  labs(caption = "OLS with type × prior. 95% intervals.") +
  theme_bw() +
  theme(legend.position = "bottom")

fig_types_by_prior
ggsave(
  file.path(fig_dir, "additional_info_types_by_prior.pdf"),
  fig_types_by_prior,
  width = 9,
  height = 6
)
```

## Pooled raw means (not in the paper)

```{r}
#| label: additional-raw-pooled

summary_pooled <-
  thirdwave |>
  mutate(
    science = info_treat,
    trust = sender_treat,
    Z = paste0(safe_time1, "/", safe_time2)
  ) |>
  transmute(
    safe_time1, safe_time2, science, trust, Z,
    credible = as.numeric(credible),
    competent = as.numeric(competent),
    correct = as.numeric(correct),
    convinced = post_mixed,
    act = behav_mixed
  ) |>
  pivot_longer(
    c(credible, competent, correct, convinced, act),
    names_to = "Y",
    values_to = "val"
  ) |>
  group_by(safe_time1, safe_time2, science, trust, Z, Y) |>
  summarise(
    n = sum(!is.na(val)),
    mean = mean(val, na.rm = TRUE),
    sd = sd(val, na.rm = TRUE),
    se = sd / sqrt(n),
    tcrit = qt(0.975, df = pmax(n - 1, 1)),
    lwr = mean - tcrit * se,
    upr = mean + tcrit * se,
    .groups = "drop"
  ) |>
  mutate(
    trust_lab = if_else(trust == 1, "high-trust institution", "low-trust institution"),
    science_lab = science_lab(science),
    cond = paste(trust_lab, science_lab, sep = "\n"),
    Z = recode(
      Z,
      "0/0" = "unsafe-unsafe",
      "0/1" = "unsafe-safe",
      "1/0" = "safe-unsafe",
      "1/1" = "safe-safe"
    ),
    Z = factor(Z, c("unsafe-unsafe", "unsafe-safe", "safe-unsafe", "safe-safe")),
    Y = factor(
      Y,
      c("competent", "credible", "correct", "convinced", "act"),
      c("competent", "credible", "correct", "belief\n(trusts mixing)", "behavior\n(would mix)")
    )
  )

raw_patterns <- ggplot(summary_pooled, aes(x = Z, y = mean)) +
  facet_grid(cond ~ Y) +
  geom_point() +
  geom_errorbar(aes(ymin = lwr, ymax = upr), width = 0.15) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Policy 1 / Policy 2", y = "")

raw_patterns
ggsave(file.path(fig_dir, "raw_patterns.pdf"), raw_patterns, width = 8, height = 8)
```

```{r}
#| label: additional-iv-first-stage-plot

tm_summary <- thirdwave |>
  mutate(
    prior = prior_group(prior_mixed),
    science = info_treat,
    trust = sender_treat,
    Z = paste0(safe_time1, "/", safe_time2),
    val = as.numeric(treatment_measurement)
  ) |>
  group_by(safe_time1, safe_time2, science, trust, Z, prior) |>
  summarise(
    n = sum(!is.na(val)),
    mean = mean(val, na.rm = TRUE),
    sd = sd(val, na.rm = TRUE),
    se = sd / sqrt(n),
    tcrit = qt(0.975, df = pmax(n - 1, 1)),
    lwr = mean - tcrit * se,
    upr = mean + tcrit * se,
    .groups = "drop"
  ) |>
  mutate(
    trust_lab = if_else(trust == 1, "high-trust institution", "low-trust institution"),
    science_lab = science_lab(science),
    cond = paste(trust_lab, science_lab, sep = "\n"),
    Z_lab = recode(
      Z,
      "0/0" = "unsafe/unsafe",
      "0/1" = "unsafe/safe",
      "1/0" = "safe/unsafe",
      "1/1" = "safe/safe"
    ),
    Z_lab = factor(Z_lab, c("unsafe/unsafe", "unsafe/safe", "safe/unsafe", "safe/safe"))
  )

raw_tm <- ggplot(tm_summary, aes(x = Z_lab, y = mean, color = prior, group = prior)) +
  facet_wrap(~cond, ncol = 2) +
  geom_point(position = position_dodge(0.45), size = 2.3) +
  geom_errorbar(
    aes(ymin = lwr, ymax = upr),
    width = 0.12,
    position = position_dodge(0.45)
  ) +
  theme_bw() +
  labs(
    x = "Policy message 1 / Policy message 2",
    y = "Perceived inconsistency (mean ± 95% CI)",
    color = "Prior"
  ) +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1))

raw_tm
ggsave(file.path(fig_dir, "iv_first_stage.pdf"), raw_tm, width = 7, height = 8)
```

## Unsaturated specification (not in the paper)

```{r}
#| label: additional-unsaturated

sat_unsat <- lapply(outcomes, function(y) {
  lm_robust(as.formula(paste(y, "~ inconsistent * trusted * science")), data = thirdwave)
})

tab_1 <- texreg::texreg(
  sat_unsat,
  include.ci = FALSE,
  custom.model.names = mod_names,
  caption = "Saturated in T1 T2 T5 only (not in paper)",
  omit.coef = c("(Intercept)"),
  stars = c(0.001, 0.01, 0.05, 0.1)
)
write(tab_1, file = file.path(fig_dir, "tab_1.tex"))
```

```{r}
#| label: additional-unsaturated-html
#| results: asis

show_htmlreg(
  sat_unsat,
  caption = "Additional (not in paper). Saturated in T1 T2 T5 only.",
  coef_map = NULL
)
```

# 7. Export

Respondent-level data are not saved. `lm_robust` objects include the estimation frame; we store coefficients and table strings only.

```{r}
#| label: export-rdata

coef_tab <- function(mods, labels = mod_names) {
  purrr::map2_dfr(mods, labels, function(m, nm) {
    tibble::tibble(
      model = nm,
      term = names(m$coefficients),
      estimate = as.numeric(m$coefficients),
      std.error = as.numeric(m$std.error)
    )
  })
}

estimates <- list(
  treatment_means = treatment_means,
  tab_sat = tab_sat,
  saturated = coef_tab(saturated),
  sat_0 = coef_tab(sat_0),
  sat_1 = coef_tab(sat_1),
  sat_priors = coef_tab(sat_priors),
  sat_low = coef_tab(sat_low),
  sat_med = coef_tab(sat_med),
  sat_high = coef_tab(sat_high),
  man_science = coef_tab(list(man_science), "science_check"),
  man_iv = coef_tab(list(man_iv), "first_stage"),
  itt = coef_tab(models_basic),
  iv = coef_tab(models_iv),
  oxcgrt_gri = coef_tab(a1_models, a1_names)
)

save(estimates, file = file.path(fig_dir, "analysis.Rdata"))
```
