---
title: "Theory figures: deemed-optimal policy and credibility"
subtitle: Predictions for the paper figures on policy support and sender credibility
format:
  html:
    number-sections: true
    embed-resources: true
    toc: true
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
---

# Setup

$\alpha$ is the probability that evidence continues to deem the same policy optimal. Underlying optimality does not change. $1-\alpha$ is the probability that new evidence leads a different policy to be *deemed* optimal. $p$ is the prior that period-1 evidence deems policy 1 optimal. $q$ is prior confidence that the sender is competent.

```{r}
#| label: theory-packages

if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman")
pacman::p_load(
  tidyverse,
  gridExtra,
  knitr,
  latex2exp
)

fig_dir <- "2_figures"
dir.create(fig_dir, showWarnings = FALSE)
```

Citizens have a prior $p$ that period-1 evidence deems policy 1 optimal. With probability $\alpha$, new evidence continues to deem the same policy optimal; with probability $1-\alpha$, new evidence leads the other policy to be deemed optimal. True optimality is fixed; only the evidence-implied (deemed) recommendation may change.

Beliefs over the deemed-optimal path $(w_1, w_2)$ are

\begin{align*}
p_{11} &= p\alpha\\
p_{10} &= p(1-\alpha) \\
p_{01} &= (1-p)(1-\alpha) \\
p_{00} &= (1-p)\alpha
\end{align*}

Without loss of generality the first signal is for policy 1.

| Event $(w_1, w_2, \theta)$ | Prior      | $\Pr(s_1 = 1, s_2=1)$ | $\Pr(s_1 = 1, s_2=0)$ |
|:--------------------------:|:----------:|:------------------:|:------------------:|
| (0, 0, 0)                  | $p_{00}(1-q)$ | $(1-r)^2$          | $r(1-r)$           |
| (0, 1, 0)                  | $p_{01}(1-q)$ | $r(1-r)$           | $(1-r)^2$          |
| (1, 0, 0)                  | $p_{10}(1-q)$ | $r(1-r)$           | $r^2$              |
| (1, 1, 0)                  | $p_{11}(1-q)$ | $r^2$              | $r(1-r)$           |
| (0, 0, 1)                  | $p_{00}q$     | $0$                | $0$                |
| (0, 1, 1)                  | $p_{01}q$     | $0$                | $0$                |
| (1, 0, 1)                  | $p_{10}q$     | $0$                | $1$                |
| (1, 1, 1)                  | $p_{11}q$     | $1$                | $0$                |

Posterior on capacity after a consistent signal $(1,1)$:

$$p^c_{11} = \frac{p_{11} q}{p_{11}q  + (p_{00}(1-r)^2 + (p_{01}+p_{10})r(1-r) + p_{11} r^2)(1-q)}$$

and after an inconsistent signal $(1,0)$:

$$p^c_{10} = \frac{p_{10} q}{p_{10} q + ((p_{00}+p_{11})r(1-r) + p_{01}(1-r)^2 + p_{10}r^2)(1-q)}$$

$p^c_{10} \leq p^c_{11}$ iff $\alpha \geq 0.5$: inconsistency is more damaging when evidence is expected to keep deeming the same policy optimal.

Posterior confidence that policy 1 is deemed optimal in period 2, given messages:

$$p^1_{11} = \frac{p_{11} q + (p_{01}r(1-r)+p_{11}r^2)(1-q)}{p_{11}q  + (p_{00}(1-r)^2 + (p_{01}+ p_{10})r(1-r) + p_{11} r^2)(1-q)}$$

$$p^1_{10} = \frac{(r(1-r)p_{11} + (1-r)^2p_{01})(1-q)}{p_{10} q + ((p_{00}+p_{11})r(1-r) + p_{01}(1-r)^2 + p_{10}r^2)(1-q)}$$

# Helpers

```{r}
#| label: theory-helpers

# α = P(deemed-optimal policy persists as evidence accumulates)
p_11 <- function(p, a) p * a
p_10 <- function(p, a) p * (1 - a)
p_01 <- function(p, a) (1 - p) * (1 - a)
p_00 <- function(p, a) (1 - p) * a

p_c_11 <- function(p, a, q, r) {
  num <- p_11(p, a) * q
  denom <- p_11(p, a) * q +
    (p_00(p, a) * (1 - r)^2 + (p_01(p, a) + p_10(p, a)) * r * (1 - r) +
       p_11(p, a) * r^2) * (1 - q)
  num / denom
}

p_c_10 <- function(p, a, q, r) {
  num <- p_10(p, a) * q
  denom <- p_10(p, a) * q +
    ((p_00(p, a) + p_11(p, a)) * r * (1 - r) + p_01(p, a) * (1 - r)^2 +
       p_10(p, a) * r^2) * (1 - q)
  num / denom
}

p_c_01 <- function(p, a, q, r) {
  num <- p_01(p, a) * q
  denom <- p_01(p, a) * q +
    ((p_00(p, a) + p_11(p, a)) * r * (1 - r) + p_01(p, a) * r^2 +
       p_10(p, a) * (1 - r)^2) * (1 - q)
  num / denom
}

p_c_00 <- function(p, a, q, r) {
  num <- p_00(p, a) * q
  denom <- p_00(p, a) * q +
    (p_00(p, a) * r^2 + (p_01(p, a) + p_10(p, a)) * r * (1 - r) +
       p_11(p, a) * (1 - r)^2) * (1 - q)
  num / denom
}

p_1_11 <- function(p, a, q, r) {
  num <- p_11(p, a) * q +
    (p_01(p, a) * r * (1 - r) + p_11(p, a) * r^2) * (1 - q)
  denom <- p_11(p, a) * q +
    (p_00(p, a) * (1 - r)^2 + (p_01(p, a) + p_10(p, a)) * r * (1 - r) +
       p_11(p, a) * r^2) * (1 - q)
  num / denom
}

p_1_10 <- function(p, a, q, r) {
  num <- (r * (1 - r) * p_11(p, a) + (1 - r)^2 * p_01(p, a)) * (1 - q)
  denom <- p_10(p, a) * q +
    ((p_00(p, a) + p_11(p, a)) * r * (1 - r) + p_01(p, a) * (1 - r)^2 +
       p_10(p, a) * r^2) * (1 - q)
  num / denom
}

p_1_01 <- function(p, a, q, r) {
  num <- p_01(p, a) * q +
    (r * (1 - r) * p_11(p, a) + r^2 * p_01(p, a)) * (1 - q)
  denom <- p_01(p, a) * q +
    ((p_00(p, a) + p_11(p, a)) * r * (1 - r) + p_01(p, a) * r^2 +
       p_10(p, a) * (1 - r)^2) * (1 - q)
  num / denom
}

p_1_00 <- function(p, a, q, r) {
  num <- (p_01(p, a) * r * (1 - r) + p_11(p, a) * (1 - r)^2) * (1 - q)
  denom <- p_00(p, a) * q +
    (p_00(p, a) * r^2 + (p_01(p, a) + p_10(p, a)) * r * (1 - r) +
       p_11(p, a) * (1 - r)^2) * (1 - q)
  num / denom
}

alpha_lab <- function(a) {
  latex2exp::TeX(paste0("$\\alpha = ", a, "$ (deemed optimum persists)"))
}
```

# Predictions

```{r}
#| label: theory-grid

df2 <- expand_grid(
  p = c(.05, .25, .5, .75, .95),
  a = c(.51, .625, .75, .875, .95),
  q = seq(.01, .99, length = 25),
  r = 2 / 3
) |>
  mutate(
    p00 = p_00(p, a),
    p01 = p_01(p, a),
    p10 = p_10(p, a),
    p11 = p_11(p, a),
    c_11 = p_c_11(p, a, q, r),
    c_10 = p_c_10(p, a, q, r),
    c_01 = p_c_01(p, a, q, r),
    c_00 = p_c_00(p, a, q, r),
    d_c = c_10 - c_11,
    pol_1_11 = p_1_11(p, a, q, r),
    pol_1_10 = p_1_10(p, a, q, r),
    pol_1_01 = p_1_01(p, a, q, r),
    pol_1_00 = p_1_00(p, a, q, r),
    d_pol_1 = pol_1_10 - pol_1_11,
    d_pol_2 = pol_1_01 - pol_1_11
  )
```

Inconsistency lowers credibility. The penalty is larger when $\alpha$ is high (new evidence is expected to keep deeming the same policy optimal) and when $q$ is middling.

```{r}
#| label: fig-credibility
#| fig-cap: "Figure 2. Theoretical predictions for credibility beliefs conditional on messaging history, prior trust in the sender (q), prior beliefs of changing evidence (α), and prior beliefs about the issue p."

fig_credibility <-
  df2 |>
  select(p, a, q, r, c_11, c_10, c_01, c_00) |>
  pivot_longer(c(c_11, c_10, c_01, c_00), names_to = "condition", values_to = "val") |>
  mutate(
    condition = factor(
      condition,
      c("c_00", "c_01", "c_10", "c_11"),
      c("0 then 0", "0 then 1", "1 then 0", "1 then 1")
    ),
    a = factor(a, unique(a), latex2exp::TeX(paste0("$\\alpha = ", unique(a), "$"))),
    p = factor(p, unique(p), latex2exp::TeX(paste0("$p = ", unique(p), "$")))
  ) |>
  ggplot(aes(q, val, color = condition)) +
  geom_line() +
  facet_grid(a ~ p, labeller = label_parsed) +
  ylab("Credibility given statement") +
  xlab("q: prior confidence in authority") +
  ggtitle("Figure 2. Credibility given messaging history") +
  labs(
    subtitle = "α = P(evidence continues to deem the same policy optimal); underlying optimality is fixed",
    caption = "r = 2/3. α high: deemed-optimal policy is expected to persist. 1−α: new evidence may deem the other policy optimal."
  ) +
  theme_bw() +
  scale_x_continuous(breaks = seq(0, 1, by = 0.25))

fig_credibility
```

```{r}
#| label: fig-policy
#| fig-cap: "Figure 1. Theoretical predictions for support for policy 1 given messaging history, prior trust in the sender (q), prior beliefs of changing evidence (α), and prior beliefs about the issue p."

fig_policy <-
  df2 |>
  select(p, a, q, r, pol_1_11, pol_1_10, pol_1_01, pol_1_00) |>
  pivot_longer(
    c(pol_1_11, pol_1_10, pol_1_01, pol_1_00),
    names_to = "condition",
    values_to = "val"
  ) |>
  mutate(
    condition = factor(
      condition,
      c("pol_1_00", "pol_1_01", "pol_1_10", "pol_1_11"),
      c("0 then 0", "0 then 1", "1 then 0", "1 then 1")
    ),
    a = factor(a, unique(a), latex2exp::TeX(paste0("$\\alpha = ", unique(a), "$"))),
    p = factor(p, unique(p), latex2exp::TeX(paste0("$p = ", unique(p), "$")))
  ) |>
  ggplot(aes(q, val, color = condition)) +
  geom_line() +
  facet_grid(a ~ p, labeller = label_parsed) +
  ylab("Support for policy 1") +
  xlab("q: prior confidence in authority") +
  ggtitle("Figure 1. Support for policy 1 given messaging history") +
  labs(
    subtitle = "α = P(evidence continues to deem the same policy optimal); underlying optimality is fixed",
    caption = "r = 2/3. High α: deemed-optimal policy expected to persist as evidence accumulates."
  ) +
  theme_bw() +
  scale_x_continuous(breaks = seq(0, 1, by = 0.25))

fig_policy
```

# Export

```{r}
#| label: theory-export

ggsave(
  file.path(fig_dir, "credibility.pdf"),
  fig_credibility,
  width = 10,
  height = 6
)

ggsave(
  file.path(fig_dir, "policy.pdf"),
  fig_policy,
  width = 10,
  height = 6
)
```
